\cvsection{Experience}
\begin{cventries}
  \cventry
    {Engineering Lead}
    {CareerBuilder, LLC}
    {Remote (Atlanta, GA)}
    {Sep. 2015 - Present}
    {
      \begin{cvitems}
        \item {Formed and led remote team that created a new, \textbf{open source CMS} (\url{github.com/cortex-cms}) designed to be \textbf{configurable, extensible, multitenant, modular and plugins-based}, while still being backed by modern technologies such as \textbf{Rails, React, Sass, GraphQL, ElasticSearch, Redis and PostgreSQL's JSONB} functionality.}
        \item {\textbf{Architected} and built foundational features, extensively detailing \textbf{implementation plans \& proposals via Github Issues} and hosting review \& feedback sessions with team, helping to avoid costly mistakes further down the road.}
        \item {Flexible \textbf{content distribution} model allowed CareerBuilder to \textbf{spin down many disparate Wordpress/Drupal installations, saving money} by reducing reliance on expensive consultants and \textbf{boosting SEO} performance by deduplicating content.}
        \item {\textbf{Mentored} team of engineers, organizing \textbf{weekly 1-on-1s}, reviewing all pull requests, \textbf{leading learning workshops}, providing constructive feedback and goals, planning and pitching team headcount, encouraging developer-contributed architecture proposals and directing all Scrum meetings.}
        \item {Built nested, multi-channel/tenant \textbf{SaaS infrastructure }to serve diverse needs across the company, bringing all content and marketing teams under a single, \textbf{unified platform} that enabled content and configuration sharing with an advanced inheritance model.}
        \item {Created content \textbf{recommendation \& relevancy} infrastructure, piping in-demand articles to job seekers through job listings and industry insight resources, solidifying CareerBuilder as a recruitment authority and increasing user base and \textbf{decreasing bounce rate.}}
        \item {Designed a Drupal-like \textbf{\textit{Content Model} system}, which allows superadministrators, on the fly, to \textbf{“lego” together} and customize various Plugin-provided \textit{Fields}, which can define validation, React, ElasticSearch and GraphQL behavior that can be further customized, per-\textit{Content Model}, by a superadministrator. Allows platform to support incredibly \textbf{flexible use cases.}}
        \item {Created Shrine-backed plugin providing \textbf{full-featured Digital Asset Management}, allowing for dynamic post-processing rules, Cloud Storage \& CDN support.}
        \item {Using dry-rb, formulated Service/Transaction Layer built around \textbf{functional, “Railway-Oriented Programming}” concepts in order to orchestrate higher-level business logic across resources and services, \textbf{simplifying unit testing and error handling.}}
        \item {Led \textbf{user testing} workshops, developing publishing \& scheduling system, on-the-fly configurable roles \& permissions, workflows and dynamic admin UI architecture in concert with content creators’ feedback.}
        \item {Built Plugin-provided \textbf{Wordpress-like WYSIWYG} editor \textbf{“Widget” system}, allowing for \textbf{referential integrity} for versioned assets, highly configurable attributes for rich content, and complex \textbf{embedded} components such as \textbf{media galleries} and video players.}
        \item {Authored \textit{Content} relation system, allowing for \textbf{complex \& configurable semantic links} (i.e. among Articles and Media) between disparate \textit{Content Models}.}
        \item {Harnessed \textbf{Docker Compose} to create a build process that transformed provisioning, environment setup and deployment into a \textbf{turnkey} process, radically \textbf{simplifying onboarding and continuous integration/deployment} steps. This also resulted in \textbf{normalized environments} across machines, reducing errors and hardening our testing process.}
        \item {Built \textbf{advanced testing harness}, allowing for core engine and plugins to be \textbf{tested independently} and easily via \textbf{CircleCI.}}
        \item {Created and \textbf{authored extensive documentation} portal (\url{docs.cortexcms.org}) for internal and external use.}
        \item {Led initiative and \textbf{produced business plan} to \textbf{open source} CMS and associated tools, fostering \textbf{community involvement and long-term maintenance} of in-house platform.}
        \\[2mm]
        \item {Created \url{hiring.careerbuilder.com}, CareerBuilder’s \textbf{employer marketing platform}, built with Rails, React, Sass, Redis and Docker on top of Cortex CMS. This new application \textbf{right-sized our revenue}, migrated purchases and subscriptions to a \textbf{brand-new self-service platform}, and \textbf{massively boosted SEO} to first-page, \textbf{top-five} performance.}
        \item {Designed and implemented composable \& configurable React- and Cortex-based widget system, \textbf{allowing frontend team} to piece together new, \textbf{rich product pages in hours} rather than days or weeks.}
        \item {Authored numerous, complex React components to \textbf{drive user conversion} during discovery \& purchase process.}
        \item {\textbf{Created} and architected on-brand, \textbf{responsive, lightweight Sass styling foundation} (similar to Bootstrap) built with \textbf{Bourbon} and \textbf{Neat} for marketing application and for use \textbf{across entire company.}}
        \item {Wrote comprehensive suite of \textbf{unit \& integration tests} using \textbf{RSpec, Capybara, Jasmine, Jest \& Enzyme}, ensuring platform stability.}
        \item {Utilized numerous tools (i.e. New Relic, Sentry, fragment/action/data caching, etc) to measure, scale and \textbf{improve site \& SEO performance}, writing numerous user stories and defect cards to address issues and technical debt.}
        \item {Built Employer Resource Center platform atop Cortex CMS, allowing \textbf{relevant marketing content} to be piped into the employer experience during the discovery \& purchase process.}
        \item {\textbf{Took over existing Shopping Cart Platform team}, overseeing resolution of performance, purchase and maintenance issues.}
        \item {\textbf{Created architecture} and plan for migration for \textbf{brownfield Shopping Cart from .NET to Rails/React}, working closely with leadership to develop next-generation purchasing platform for CareerBuilder.}
      \end{cvitems}
    }
\end{cventries}
